Visualizations for the manuscript

### 2022-10-18 metanalysis_visualization/manuscript_Figures.Rmd
- Fixing plots: 	- Expanding predictions from bootstrap model 	- Adapting x-axis scale - Cleaning code to have consistent time/time_p throughout the file

```{r}
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>% 
  mutate(count_icd = count_no_psy_patients + count_psy_patients)

@@

```{r}
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")

@@

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 100
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

bootstrapping_slopes <- function(df,
                                 group_name,
                                 bootstrap_size,
                                 count = "count_icd",
                                 percentage = "percentage") {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = as.integer(df[[count]]),
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- df$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>%
    bind_cols(group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                            .id = "iteration") %>%
    bind_cols(group_name)
  return(list(bootstrapped_coefficients_df,
              bootstrapped_fitted_df))
}
```

@@

```{r, fig.width = 20, fig.height=14}
bootstrapped_fitted_all %>%
  # mutate( time = time + 0.5) %>%

          # 
          # ),
          # time_p = as.character(time_p),
          #         time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
          #         time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
          #         time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
          #         time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
          #         time_p = as.Date(time_p))%>%
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE), ncol = 2) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            # %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
            #       time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
            #       time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
            #       time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
            #       time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
            #       time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  # geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ] 
  #           %>% mutate(time_p = as.Date(time_p)+ 15, 
  #                      time_p = as.character(time_p),
  #                 time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
  #                 time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
  #                 time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
  #                 time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
  #                 time_p = as.Date(time_p)),
  #           aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             # %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_x_continuous(breaks = scales::breaks_width(1, offset = 0)) + 
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

# ggsave("figure1_boostrapped_all.png", height = 20, width = 25, units = "cm")
```

```{r}
bootstrapped_fitted_all %>%
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE), ncol = 2) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ] 
            %>% mutate(time_p = as.Date(time_p)+ 15, 
                       time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                xlab = "Mean of the coefficients",
                mlab="Overall effect")
dev.off()
#ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")
```

@@

forest.meta(m.siteid, 
            sortvar = TE,
            print.tau2 = FALSE,
            leftlabs = c("plotsLabel"))

forest.meta(m.siteid, layout = "JAMA")
```

@@

```{r, include=FALSE}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, sex ) %>%
  summarise( total = sum( count ), 
             count_sex = sum( count_sex ), 
             percentage = 100* count_sex / total, 
             siteid = "ALL") %>%  
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count_sex, percentage, siteid)
```

@@

```{r}
observed_coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation, 
               slope_name = c("time", "periodduring_pandemic:time")
               ) %>% 
  rename(observed_slope_coefficient = estimate) %>% 
  pivot_wider(names_from = term,
              values_from = observed_slope_coefficient) %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`) %>% 
  mutate(during_slope = before_slope + difference_slope) %>% 
  pivot_longer(cols = c(before_slope, difference_slope, during_slope), 
               names_to = "term", 
               values_to = "observed_slope_coefficient")

@@

```{r }
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_map(~ bootstrapping_slopes(.x,
                                   group_name = .y,
                                   bootstrap_size = bootstrap_size,
                                   count = "count_sex", 
                                   percentage = "percentage"))

@@

ci_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("(95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), ")"))

@@

quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

@@

```{r}
pvalues_boot_sex_complete <- pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  #mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  mutate(string = paste0(observed_slope_coefficient, "% ", ci)) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-3), ")")) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope) %>% 
  flextable::flextable() %>% 
  flextable::save_as_docx(path = "table_sex.docx")

@@

```{r}
#plot_annotations_sex_df <- pvalues_boot_sex %>%
#  select(term, sex, label) %>% 
#  filter(term == "difference_slope" & sex == "female") %>% 
#  mutate(plotsLabel = "Female")

plot_annotations_sex_df <- pvalues_boot_sex_complete %>%
  filter( sex == "female") %>% 
    mutate(plotsLabel = "Female") %>%
  select( label = `Difference before/since pandemic trend [95% CI] (p-value)`, plotsLabel )

```{r }
#plot_annotations_sex_df2 <- data.frame(term=c("difference_solpe","difference_solpe"),
#                                       sex=c("female", "male"),
#                                       label=c("Coefficient difference: 0.77 (pvalue: <0.01)", "Coefficient difference: -0.77 (pvalue: 0.005)"),
#                                       plotsLabel=c("Female", "Male"))

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ] %>% 
              mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ]%>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",]  
             %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

perc_disorder_group_total <- perc_disorder_group_complete %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             dg_cases = sum(count_dg),
             percentage = (dg_cases / total_diagnoses) * 100, 
             country = "ALL", 
             siteid = "ALL") %>% 
  mutate(period = ifelse(time_p < pandemic_start_date,
                         "before_pandemic", 
                         "during_pandemic")) %>% 
    filter(disorder_group %in% disorders_to_select)

@@

ci_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("(95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), ")"))

@@

percentages_htm <- percentages_htm[  , -1]

>>>>

```{r}
# To be able to have one single reference for the mapping between periods, months and months labels
time_timep_df <- distinct(patient_count_psy_period_psy_all[, c("time", "time_p")])
time_timep_list <- time_timep_df[["time_p"]]
names(time_timep_list) <- as.character(time_timep_df[["time"]])
time_timep_list[["29"]] <- as.Date("2021-05-01")
```

```{r}
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>% 
  mutate(count_icd = count_no_psy_patients + count_psy_patients)
patients_hospitalized_agg_sex_perc_all <- left_join(
  patients_hospitalized_agg_sex_perc_all, 
  time_timep_df, 
  by = c("time_p"))
perc_disorder_group_all <- left_join(perc_disorder_group_all, 
                                     time_timep_df, 
                                     by = c("time_p"))
```

@@

```{r}
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")
```

@@

```{r}
bootstrap_size <- 10000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

bootstrapping_slopes <- function(df,
                                 group_name,
                                 bootstrap_size,
                                 count = "count_icd",
                                 percentage = "percentage") {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = as.integer(df[[count]]),
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               time_p = df$time_p,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    # To be able to fill the gap in the subsequent graphs
    df_extended_prediction <- data.frame(
      period = c("before_pandemic", "before_pandemic", "during_pandemic", "during_pandemic"), 
      time = c(1.5, 15.5, 15.5, 28.5), 
      time_p = NA,
      percentage = NA
    )
    df_iteration <- bind_rows(df_iteration, df_extended_prediction)
    df_iteration$predicted <- predict(ts_linear_percent, newdata = df_iteration)
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>%
    bind_cols(group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                            .id = "iteration") %>%
    bind_cols(group_name)
  return(list(bootstrapped_coefficients_df,
              bootstrapped_fitted_df))
}
```

@@

```{r}
# Function to change x-axis labels in graphs
time_to_time_p <- function(break_ticks) {
  break_ticks <- as.character(break_ticks)
  sapply(break_ticks, function(break_tick) {
   if (is.na(break_tick) | !break_tick %in% names(time_timep_list)) {
     return(as.Date(NA_character_))
   } else {
     time_timep_list[[break_tick]]
   }
  }) %>%
    as.Date(origin = "1970/01/01") %>% 
    format(format = "%b %Y", tz = "UTC")
}

```{r, fig.width = 20, fig.height=14}
bootstrapped_fitted_all %>%
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE), ncol = 2) +
  geom_line(aes(x = time + 0.5, color = period), alpha = 0.03) +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = interaction(quantiles, period)),
            data = filter(quantile_bootstrapped_fitted_all, quantiles %in% c("2.5%", "97.5%")),
            linetype = "dashed") +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = period),
            data = filter(quantile_bootstrapped_fitted_all, quantiles == "50%")) +
  geom_point(aes(x = time + 0.5, y = percentage, group = NULL),
             data = patient_count_psy_period_psy_all,
             alpha = 0.5) +
  scale_x_continuous(breaks = breaks_width(1),
                     labels = time_to_time_p, 
                     limits = c(2, 29),
                     expand = c(0.03,0)) + 
  geom_vline(xintercept = 16, linetype = 6 ) +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom") + 
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period")

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                xlab = "Mean of the coefficients",
                mlab="Overall effect")
dev.off()
```

@@

forest.meta(m.siteid, 
            sortvar = TE,
            print.tau2 = FALSE,
            leftlabs = c("plotsLabel"))
forest.meta(m.siteid, layout = "JAMA")

@@

```{r, include=FALSE}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, time, sex ) %>%
  summarise( total = sum( count ), 
             count_sex = sum( count_sex ), 
             percentage = 100* count_sex / total, 
             siteid = "ALL") %>%  
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  mutate(month_year = format(time_p, "%m")) %>% 
  select(time_p, time, period, sex, count_sex, percentage, siteid, month_year)
```

@@

```{r}
observed_coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  group_modify(coefficient_slope_calculation, 
               slope_name = c("time", "periodduring_pandemic:time")
               ) %>% 
  rename(observed_slope_coefficient = estimate) %>% 
  pivot_wider(names_from = term,
              values_from = observed_slope_coefficient) %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`) %>% 
  mutate(during_slope = before_slope + difference_slope) %>% 
  pivot_longer(cols = c(before_slope, difference_slope, during_slope), 
               names_to = "term", 
               values_to = "observed_slope_coefficient")

@@

```{r }
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  group_map(~ bootstrapping_slopes(.x,
                                   group_name = .y,
                                   bootstrap_size = bootstrap_size,
                                   count = "count_sex", 
                                   percentage = "percentage"))

@@

ci_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975), 
            .groups = "drop") %>% 
  mutate(ci = paste0("(95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), ")"))

@@

quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, time, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975), 
            .groups = "drop") %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

@@

```{r}
pvalues_boot_sex_complete <- pvalues_boot_sex %>% 
  inner_join(ci_boot_sex, by = c("sex", "term")) %>% 
  arrange(sex) %>% 
  #mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  mutate(string = paste0(observed_slope_coefficient, "% ", ci)) %>% 
  select(sex, string, term) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

pvalues_boot_sex %>% 
  inner_join(ci_boot_sex, by = c("sex", "term")) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-3), ")")) %>% 
  select(sex, string, term) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope) %>% 
  flextable::flextable() %>% 
  flextable::save_as_docx(path = "table_sex.docx")

@@

```{r}
plot_annotations_sex_df <- pvalues_boot_sex_complete %>%
  filter( sex == "female") %>% 
    mutate(plotsLabel = "Female") %>%
  select( label = `Difference before/since pandemic trend [95% CI] (p-value)`, plotsLabel, sex)
```

```{r }
bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(x = time + 0.5, color = period), alpha = 0.01) +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = interaction(quantiles, period)),
            data = filter(quantile_bootstrapped_fitted_sex, sex == "female" & quantiles %in% c("2.5%", "97.5%")),
            linetype = "dashed") +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = period),
            data = filter(quantile_bootstrapped_fitted_sex, sex == "female" & quantiles == "50%")) +
  geom_point(aes(x = time + 0.5, y = percentage, group = NULL),
             data = filter(patients_hospitalized_agg_sex_total, sex == "female"),
             alpha = 0.5) +
  scale_x_continuous(breaks = breaks_width(1),
                     labels = time_to_time_p, 
                     limits = c(2, 29),
                     expand = c(0.03,0)) + 
  geom_vline(xintercept = 16, linetype = 6 ) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom")

ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

perc_disorder_group_total <- perc_disorder_group_complete %>%
  group_by( time_p, time, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             dg_cases = sum(count_dg),
             percentage = (dg_cases / total_diagnoses) * 100, 
             country = "ALL", 
             siteid = "ALL") %>% 
  mutate(period = ifelse(time_p < pandemic_start_date,
                         "before_pandemic", 
                         "during_pandemic")) %>% 
  filter(disorder_group %in% disorders_to_select)

@@

ci_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975), 
            .groups = "drop") %>% 
  mutate(ci = paste0("(95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), ")"))

@@

percentages_htm <- percentages_htm %>% select(-time, -time_p)
